\renewcommand{\abstractname}{Acknowledgement}
\renewcommand{\abstractnamefont}{\Huge\textbf}
\renewcommand{\abstracttextfont}{\normalsize}

\begin{abstract}

\OnehalfSpacing

The satisfaction that accompanies the successful completion of our project would be incomplete without mentioning the people who made it possible, whose constant guidance and encouragement crowns all the efforts with success.

We would greatly mention the enthusiastic influence for provided by Dr. Krishnan R., Professor, Department of Computer of Science and Engineering of Dayananda Sagar College of Engineering for his ideas and co-operation during our venture and making this project a great success.

We are thankful to Dr. D. R. Ramesh Babu, Vice-Principal \& HoD of Department of Computer Science and Engineering of Dayananda Sagar College of Engineering for his co-operation during all phases of our project.

We are also thankful to Dr. C. P. S. Prakash, Principal of Dayananda Sagar College of Engineering, Bangalore for being kind enough to provide us an opportunity to work on a project in this institution.

It is a pleasure to thank the friendly co-operation showed by all the staff members of the Computer Science Department, Dayananda Sagar College of Engineering, and finally, not to forget our friends \& family who have supported us through our academic career.

\vspace{2cm}

\begin{flushleft}
Raja Rajan A.\\
Varsha Jambunathan\\
Laasya R.\\
\end{flushleft}

\vfill

\end{abstract}
